Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-04 Experiments.tex

\begin{figure}[!htb]
        \includegraphics[height=4.5cm,width=\columnwidth]{./figures/NGE/weak1.pdf}
    \caption{Weak scalability: average pilot duration, average  duration of a
    single AthenaMP execution, and pilot's overhead as a function of pilot sizes (200, 500, 1000 and 2000 nodes).}
\label{fig:weakScal1a}
\end{figure}

@@

\begin{figure}[!htb]
        \includegraphics[height=4.5cm,width=\columnwidth]{./figures/NGE/weak2.pdf}
    \caption{Weak scalability with multiple generations: average pilot
    duration, average duration of five sequential AthenaMP executions, and
    pilot's overhead for pilot sizes (256, 512, 1024 and 2048 nodes).}
\label{fig:weakScal2a}
\end{figure}

@@

\begin{figure}[!htb]
        \includegraphics[height=4.5cm,width=\columnwidth]{./figures/NGE/strong.pdf}
    \caption{Strong scalability:  average pilot duration, average duration of
    sequential AthenaMP executions, and pilot's overhead for different pilot
    sizes (256, 512, 1024 and 2048 nodes).}
\label{fig:strongScala}
\end{figure}

>>>>

\begin{figure}[!htb]
        \includegraphics[height=4.5cm,width=\columnwidth]{./figures/NGE/weak1.pdf}
    \caption{Weak scalability: average pilot duration, average duration of one AthenaMP execution, and pilot's overhead as a function of pilot sizes (200, 500, 1000 and 2000 nodes).}
\label{fig:weakScal1a}
\end{figure}

@@

\begin{figure}[!htb]
        \includegraphics[height=4.5cm,width=\columnwidth]{./figures/NGE/weak2.pdf}
    \caption{Weak scalability with multiple generations: average pilot
    duration, average duration of sequential AthenaMP executions, and
    pilot's overhead for pilot with 256, 512, 1024 and 2048 nodes.}
\label{fig:weakScal2a}
\end{figure}

@@

\begin{figure}[!htb]
        \includegraphics[height=4.5cm,width=\columnwidth]{./figures/NGE/strong.pdf}
    \caption{Strong scalability:  average pilot duration, average duration of
    sequential AthenaMP executions, and pilot's overhead for pilots with 256, 512, 1024 and 2048 nodes.}
\label{fig:strongScala}
\end{figure}

### 2017-04-04 PandaOverview.tex

PanDA's application model assumes tasks grouped into workloads and workflows.
Tasks represent a set of operations performed on data sets stored in one or more
input files. Tasks are decomposed into jobs, where each job consists of the
task's operations performed on a partition of the task's data set. Since 2005, a
certain amount of parallelism has been progressively introduced for job
execution~\cite{crooks2012multi} but, so far, HEP applications have not required
MPI.
% Jobs are supposed to be capable of setting up their own execution
% environment and have a minimal set of common dependences.

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/panda_architecture.pdf}
    \caption{PanDA WMS architecture. Numbers indicates the JEDI-based execution
    process. Several subsystems, components, and architectural and
    communication details are abstracted for clarity.}
\label{fig:architecture}
\end{figure}

>>>>

PanDA's application model assumes tasks grouped into workloads and workflows.
Tasks represent a set of operations performed on data sets stored in one or more
input files. Tasks are decomposed into jobs, where each job consists of the
task's operations performed on a partition of the task's data set. Since 2005, a
certain amount of parallelism has been progressively introduced for job
execution~\cite{crooks2012multi} but, so far, HEP applications have not required
a message passing interface (MPI).
% Jobs are supposed to be capable of setting up their own execution
% environment and have a minimal set of common dependences.

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/panda_architecture.pdf}
    \caption{PanDA WMS architecture. Numbers indicates the JEDI-based execution
    process. Several subsystems, components, and architectural and
    communication details are abstracted to improve clarity.}
\label{fig:architecture}
\end{figure}

### 2017-04-04 nge.tex
saved 4-5 lines and minor corrections.

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{figures/rp_architecture_compact_atlaswms_paper.pdf}
  \caption{NGE Architecture as deployed on Titan. The PilotManager and the
  UnitManager reside on one of Titan's DTN while the Agent is executed on
  Titan's worker nodes. Boxes color coding: gray for entities external to NGE,
  white for APIs, purple for NGE's modules, green for pilots, yellow for
  module's components.}
\label{fig:arch-overview}
\end{figure}

>>>>

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{figures/rp_architecture_compact_atlaswms_paper.pdf}
  \caption{NGE Architecture: The PilotManager and  UnitManager reside on a Titan
  DTN while the Agent is executed on its worker nodes. Color coding: gray for
  entities external to NGE, white for APIs, purple for NGE's modules, green for
  pilots, yellow for module's components.}
\label{fig:arch-overview}
\end{figure}

### 2017-04-04 overall.tex

\begin{figure*}%[htp]
    \includegraphics[clip,width=0.32\textwidth]{figures/titan_backfill_wnodes_distribution.pdf}
    \includegraphics[clip,width=0.32\textwidth]{figures/titan_backfill_walltime_distribution.pdf}
    \includegraphics[clip,width=0.32\textwidth]{figures/titan_backfill_avail.png}
    \caption{Backfill availability: distribution of number of work nodes (left);
    distribution of walltime in minutes (center); and a scatter plot of the two
    variables (right). 62175 measures: mean number of work nodes available 691;
    mean walltime available 126 minutes.}
\label{fig:backfill-distrib}
\end{figure*}

@@

\begin{figure}[htp]
    \includegraphics[clip,width=\columnwidth]{figures/tx8_tx16_comparison_vsquashed.pdf}
    \caption{Comparison between distributions of the time taken by a Geant4
    detector simulation to simulate one event when placing 2 simulations (h1) or
    1 simulation (h2) per CPU. 2 simulation use 16 cores per node, 1 simulation
    8, 1 per compute unit. 50 Events; 1 Titan worker nodes; 16 work threads per
    node; 100 events per node.}
\label{fig:comparison-8-16cores}
\end{figure}

>>>>

\begin{figure*}%[htp]
    \includegraphics[clip,width=0.32\textwidth]{figures/titan_backfill_wnodes_distribution.pdf}
    \includegraphics[clip,width=0.32\textwidth]{figures/titan_backfill_walltime_distribution.pdf}
    \includegraphics[clip,width=0.32\textwidth]{figures/titan_backfill_avail.png}

    \caption{Backfill availability: distribution of number of work nodes (left)
    and of walltime in minutes (center). Scatter plot of the two variables
    (right). 62175 measures: mean number of work nodes available 691; mean
    walltime available 126 minutes.}

\label{fig:backfill-distrib}
\end{figure*}

@@

\begin{figure}[htp]
    \includegraphics[clip,width=\columnwidth]{figures/tx8_tx16_comparison_vsquashed.pdf}

    \caption{Distributions of the time taken to simulate one event when placing
    2 simulations (h1) or 1 simulation (h2) per Titan's CPU. 2 simulation use 16
    cores per node, 1 simulation 8. 50 Events; 1 Titan worker nodes; 16 work
    threads per node; 100 events per node.}

\label{fig:comparison-8-16cores}
\end{figure}
